---
title: "To BTO or not to BTO"
author: "Wesley Chioh"
date: "12/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(mapboxapi)
library(plotly)
library(kableExtra)
library(httr)
library(jsonlite)
library(tidyjson)

## It is not worth the trouble
# # URA API Access
# 
# ## Setting up URA API Access Token
# ura_token <- read_csv("URA_Token.txt", col_names = F) %>%
#   unlist(use.names = F)
# ura_daily_access <- GET(url = "https://www.ura.gov.sg/uraDataService/insertNewToken.action", 
#                         add_headers(AccessKey = ura_token)) %>%
#   content() %>%
#   unlist(.,use.names = F) %>%
#   .[3]
# 
# ## Getting data from URA
# ura_private_property_transaction_records_1 <- GET(url = "https://www.ura.gov.sg/uraDataService/invokeUraDS?service=PMI_Resi_Transaction&batch=1",
# add_headers(AccessKey = ura_token, Token = ura_daily_access)) %>%
#   content()
# ura_batch1 <- ura_private_property_transaction_records_1[2]
# ura_batch1 <- data.frame(t(sapply(ura_private_property_transaction_records_1,c)))


```

## Primer

The Singapore real estate market has been red-hot this past year, Covid-19 induced economic tremors notwithstanding. Invariably, Singaporeans buy property as a store of wealth, an investment that is both income-generating and capital gain generating. More troubling is the fact that some Singaporeans see HDB subsidised apartments as such a vehicle as well.  
  
The questions at hand, are therefore:  
1. What has the trend been, where property prices are concerned in Singapore? Is there a difference between private and public housing options, after controlling for sizes and district?  
2. What are some of the factors affecting property prices in Singapore? Is it proximity to amenities?  
3. Can we predict housing prices using HDB and URA data sets?  
4. Are there any hidden gems?  

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
